Working title, The impact of heterospecific pollen on plant reproductive success is mediated by phylogenetic distance and floral reproductive traits

### 2018-12-03 Manuscript_draft/Manuscript_draft.Rmd
last things of today

Recent studies have advanced in the ecological importance of heterospecific pollen effect @morales2008 @ashman2013 @arceo2016. A general overview of foreign pollen arrival is that it can play an important role on species fitness but seems to be context dependent and not always produce a decrease in fitness @morales2008. Part of this unpredictability is due to the enormous variability of foreing pollen transferred in nature, where levels between 0 and 75 percent are seen, but most commonly values ranges between 10 and 20 percent of the total pollen load, being the generalist species the ones that receive greater loads of heterospecific pollen @montgomery2012 @fang2013. Although heterospecific pollen quantity is fundamental to understand the outcome of the interaction so is the different traits of both pollen donor and recipient. @ashman2013 postulated the first predictive framework for traits of heterospecific pollen effect where traits such as compatibility system and pollen size among others should be crucial to understand foreing pollen effect. Moreover,  in @tong2016 a assymetric effect was shown in a crossing experiment between 6 species of the genus *Pedicularis* where the pollen of long styled species was able to grow the ful length of the syle on short styled species but not viceversa. Despite these recent caveats, we still lack empirical evidence to affirm what are the main traits that drive heterospecific pollen effect for both pollen donor and recipient at seed production level. Interestingly, this trait based question cannot be solved without consider the phylogenetic relatedness of the species. A commonly understanding is that close related species will have greater negative impact

>>>>

Recent studies have advanced in the ecological understanding of heterospecific pollen effect @morales2008 @ashman2013 @arceo2016. A general overview of foreign pollen arrival is that it can play an important role on species fitness but seems to be context dependent and not always produce a decrease in fitness @morales2008. Part of this unpredictability is due to the enormous variability of foreing pollen transferred in nature, where levels between 0 and 75 percent are seen, but most commonly values ranges between 10 and 20 percent of the total pollen load, being the generalist species the ones that receive greater loads of heterospecific pollen @montgomery2012 @fang2013. Although heterospecific pollen quantity is fundamental to understand the outcome of the interaction so is the different traits of both pollen donor and recipient. @ashman2013 postulated the first predictive framework for traits of heterospecific pollen effect where traits such as compatibility system and pollen size among others should be crucial to understand foreing pollen effect. Moreover, in @tong2016 a assymetric effect was shown in a crossing experiment between 6 species of the genus *Pedicularis* where the pollen of long styled species was able to grow the ful length of the style on short styled species but not viceversa. Despite these recent caveats, we still lack empirical evidence to affirm what are the main traits that drive heterospecific pollen effect for both pollen donor and recipient at seed production level. Interestingly, this trait based question of effect between a pair of species cannot be solved without consider the phylogenetic relatedness of them. A general view is that close related species will have greater negative impact than far related species (REFS). Muchas especies inclusos congeneres difieren en traits

Plenty of work have consider crosses between close related species, showing both negative and none effect. One of the concerns at seed set level is that in case that species are able to hybridised the negative impact of heterospecific pollen effect is hidden.
